Table on stock change factors per clinate zone

### 2022-10-21 ResultNotebooks/results_SOCscattervalidate.Rmd
update Images

dev.copy(png, paste0(outputdir, "scatterCompareSoilGrids2_2010_lu.png"), width = 1500, height = 1500, res = 250)
dev.off()

@@

  out <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(data, Year == "2010", c("lon", "lat", "Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name     = name,
                      values   = cols,
                      labels   = labels,
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size = legend_size),
                        direction      = "horizontal",
                        title.position = "top",
                        # I shift the labels around, the should be placed
                        # exactly at the right end of each legend key
                        title.hjust    = 0.5,
                        label.hjust    = 1,
                        nrow           = 1,
                        byrow          = FALSE,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          axis.title.x     = element_blank(),
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7, 0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

cols              <- c("#648FFF", "#DC267F", "#FFB000")[c(1, 3, 2)]
SoilGrids2InMap   <- SOCplotmap(data     =  soilgrid22plot,
                                 limits   = c(0.5, 1.5),
                                 cols     = cols,
                                 name     = expression("Modeled SOC stock in relation to uncertainty range of SoilGrids 2.0"),
                            breaks   = c(0.5, 1.0, 1.5),
                            labels   = c("lower than Q0.05", "inside [Q0.05, Q0.95] ", "higher than Q0.95", "No Cropland"))

SoilGrids2InMap
ggsave(paste0(outputdir, "/SOCquantilesSoilGrids2.png"),    plot = SoilGrids2InMap,    width = 15, height = 10, dpi = 300, units = "cm")
```

>>>>

dev.copy(png, paste0(outputdir, "scatterCompareSoilGrids2_2010_lu.png"), width = 1300, height = 1300, res = 250)
dev.off()

@@

  out <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(data, Year == "2010", c("lon", "lat", "Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name     = name,
                      values   = cols,
                      labels   = labels,
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size = legend_size),
                        direction      = "horizontal",
                        title.position = "top",
                        # I shift the labels around, the should be placed
                        # exactly at the right end of each legend key
                        title.hjust    = 0,
                        label.hjust    = 0,
                        nrow           = 1,
                        byrow          = FALSE,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.margin    = margin(t = 0, r = 0, b = 0, l = 1, unit = "cm"),
          axis.title.x     = element_blank(),
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7, 0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

cols              <- c("#648FFF", "#DC267F", "#FFB000")[c(1, 3, 2)]
SoilGrids2InMap   <- SOCplotmap(data     =  soilgrid22plot,
                                limits   = c(0.5, 1.5),
                                cols     = cols,
                                name     = NULL,
                                breaks   = c(0.5, 1.0, 1.5),
                                labels   = c("< Q0.05", "inside [Q0.05, Q0.95] ", "> Q0.95", ""))

SoilGrids2InMap
ggsave(paste0(outputdir, "/SOCquantilesSoilGrids2.png"),    plot = SoilGrids2InMap,    width = 10, height = 7, dpi = 400, units = "cm")
```

### 2022-10-21 ResultNotebooks/results_SOCscenario.Rmd
update Images

vSOCemis <- 
  ggplot() + geom_line(data = as.data.frame(-glo_SOCDebt[, years, manage_scen]),  
                       aes(x = Year, y = Value, group = Data1, color = Data1)) +
  labs(x = "Year", y = expression(paste("Global \u0394SOC in GtC")),
       color = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values = scen_cols, labels = names(manage_scen)) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size),
        legend.position = "right", legend.direction = "vertical")

vSOCinput <- 
  ggplot(data = as.data.frame(glo_SOCInput[, years, c(3:4, 2, 1)]),  
         aes(x = Year, y = Value, group = Data1, fill = Data1)) + geom_area() +
  labs(x = "Year", y = "SOC input in tC per ha\n (global average)", fill = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous() +
  scale_fill_manual(values = input_cols) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size), 
        legend.direction = "vertical")

@@

vgrid <- plot_grid(plot_grid(vSOCemis  + theme(legend.position = "none"),
                             vSOCinput + theme(legend.position = "none"), 
                             ncol = 1, labels = c("(a)", "(b)"),
                             label_fontface = "plain", label_size = 10, 
                             align = "v", axis = "tblr"),
                   plot_grid(get_legend(vSOCemis), get_legend(vSOCinput), 
                             ncol = 1, label_fontface = "plain", 
                             label_size = 10, align = "v"),
                   align = "h")

@@

ggsave(paste0(outputdir, "Images/scenario_horiz.png"), 
       plot = hgrid, width = 15, height = 10, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "Images/scenario_verti.png"), 
       plot = vgrid, width = 12, height = 15, dpi = 300, units = "cm")
```

>>>>

vSOCemis <- 
  ggplot() + geom_line(data = as.data.frame(-glo_SOCDebt[, years, manage_scen]),  
                       aes(x = Year, y = Value, group = Data1, color = Data1)) +
  labs(x = "Year", y = expression(paste("Global \u0394SOC in GtC")),
       color = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values = scen_cols, labels = names(manage_scen)) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size),
        legend.position = "right", legend.direction = "vertical",
        legend.margin = margin(0, 0, -1, 0),
        legend.box.margin = margin(0, 0, 0, -20))

vSOCinput <- 
  ggplot(data = as.data.frame(glo_SOCInput[, years, c(3:4, 2, 1)]),  
         aes(x = Year, y = Value, group = Data1, fill = Data1)) + geom_area() +
  labs(x = "Year", y = "SOC input in tC per ha\n (global average)", fill = "") +
  scale_x_discrete(breaks = seq(1975, 2010, 5)) +
  scale_y_continuous() +
  scale_fill_manual(values = input_cols) +
  theme(rect = element_blank(),
        axis.title.y = element_text(size = legend_size, 
                                    margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.title.x = element_text(size = legend_size, 
                                    margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                    unit = "pt")),
        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, 
                                   size = legend_size), 
        legend.direction = "vertical", 
        legend.margin = margin(-140, 0, 0, 0),
        legend.box.margin = margin(0, 0, 0, -20))

@@

vgrid <- plot_grid(plot_grid(vSOCemis  + theme(legend.position = "none"),
                             vSOCinput + theme(legend.position = "none"), 
                             ncol = 1, labels = c("(a)", "(b)"),
                             label_fontface = "plain", label_size = 10, 
                             align = "v", axis = "tblr"),
                   plot_grid(get_legend(vSOCemis), get_legend(vSOCinput), 
                             ncol = 1, label_fontface = "plain", 
                             label_size = 10, align = "v"),
                   align = "h", rel_widths = c(1.4, 1))

@@

ggsave(paste0(outputdir, "Images/scenario_horiz.png"), 
       plot = hgrid, width = 15, height = 10, dpi = 300, units = "cm")
ggsave(paste0(outputdir, "Images/scenario_verti.png"), 
       plot = vgrid, width = 13, height = 15, dpi = 300, units = "cm")
```

### 2022-10-21 ResultNotebooks/results_SOCtable.Rmd
update Images

climateIPCCr <- readRDS(paste0("Data/", rev, scen, "/IPCC_reduced.rds"))
climateIPCC  <- readRDS(paste0("Data/", re, scen, "/IPCC.rds"))

@@

magpie_coord <- toolGetMapping("magpie_coord.rda", type = "cell")
climate2plot <- dimSums(climateIPCC * 
                          new.magpie("GLO", NULL, 
                                     getNames(climateIPCC), 
                                     c(1:12)), 
                        dim = 3)
climate2plot <- merge(as.data.frame(climate2plot), 
                      data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")

@@

```{r table2boxplot, fig.height=3, fig.width=6}

@@

cols <- c("#648FFF", "#DC267F", "#FFB000")[3:1]

SCFTable <- 
  ggplot() + 
    geom_linerange(data = range_table,
                   aes(x = Region, ymin = Q0p05, ymax = Q0p95, color = Source),
                   position = position_nudge(x = 0.165), size = 0.6) +
    geom_point(data = comparison_table, 
               aes(y = Data, x = Region, group = Source, color = Source, shape = Management), 
               position = position_dodge(width = 0.5), 
               size = 2) +
    labs(y = "Stock Change Factor",
         x = "Climate Zone") +
    scale_color_manual(values = cols) +
    guides(shape = guide_legend(order = 2),col = guide_legend(order = 1)) +
    theme(rect = element_blank(),
                        axis.title.y = element_text(size = legend_size,
                                                   margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                                   unit = "pt")),
                        axis.title.x = element_text(size = legend_size,
                                                   margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                                   unit = "pt")))

ggsave(paste0(outputdir, "Images/SCF_comparison.png"), 
       plot = SCFTable, height = 8, width = 18, units = "cm", dpi = 300)
```

>>>>

climateIPCCr <- readRDS(paste0("Data/", rev, scen, "/IPCC_reduced.rds"))
climateIPCC  <- readRDS(paste0("Data/", rev, scen, "/IPCC.rds"))

@@

magpie_coord <- toolGetMapping("magpie_coord.rda", type = "cell", where="mappingfolder")
climate2plot <- dimSums(climateIPCC * 
                          new.magpie("GLO", NULL, 
                                     getNames(climateIPCC), 
                                     c(1:12)), 
                        dim = 3)
climate2plot <- merge(as.data.frame(climate2plot), 
                      data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")

@@

```{r table2boxplot, fig.height=3, fig.width=6}
library(ggplot2)

@@

cols        <- c("#648FFF", "#DC267F", "#FFB000")[3:1]
legend_size <- 12

SCFTable <- 
  ggplot() + 
    geom_linerange(data = range_table,
                   aes(x = Region, ymin = Q0p05, ymax = Q0p95, color = Source),
                   position = position_nudge(x = 0.165), size = 0.6) +
    geom_point(data = comparison_table, 
               aes(y = Data, x = Region, group = Source, color = Source, shape = Management), 
               position = position_dodge(width = 0.5), 
               size = 2) +
    labs(y = "Stock Change Factor",
         x = "Climate Zone") +
    scale_color_manual(values = cols) +
    scale_x_discrete(labels = c("tropical\nmoist", "tropical\ndry", 
                                "temperate\ndry",  "temperate\nmoist")) +
    guides(shape = guide_legend(order = 2),col = guide_legend(order = 1)) +
    theme(rect = element_blank(),
          axis.title.y = element_text(size = legend_size,
                                      margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                                   unit = "pt")),
          axis.title.x = element_text(size = legend_size,
                                      margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                                   unit = "pt")),
          axis.text.x  = element_text(size = legend_size),
          axis.text.y  = element_text(size = legend_size),
          legend.title = element_text(size = legend_size),
          legend.text  = element_text(size = legend_size),
          legend.spacing.y = unit(0.1, "cm"),
          legend.position="bottom",
          legend.direction = "vertical",
          legend.box = "horizontal"
          )

SCFTable

ggsave(paste0(outputdir, "Images/SCF_comparison.png"), 
       plot = SCFTable, height = 11, width = 17, units = "cm", dpi = 300)
```
